---
title: "Populist Narratives on Environmental Issues in the Media: A Discourse Analysis"
subtitle: "Capstone Project in Data Mining and Large Language Models for Political and Social Sciences"
author: 
  - "Alessia Rainone, alessia.rainone@stud.unilu.ch, 20-118-808"
  - "Supervisor: Prof. Dr. Andrea De Angelis"
  - "Number of words: 1XX"
lang: en
date: today
date-format: "D. MMMM YYYY"
format: 
  pdf:
    documentclass: scrreprt
    number-sections: true
    toc: false
    toc-depth: 2
    lot: false
    include-in-header:
      - text: |
          \usepackage{authblk}
          \usepackage{titling}
fontsize: 12pt
linestretch: 1.5
geometry: left=2.5cm,right=2.5cm,top=3cm,bottom=3cm
citeproc: true
execute:
  echo: false
  warning: false
knitr:
  opts_chunk:
    message: false
lof: true
lot: true
---

# Abstract {.unnumbered}

This project attempts to answer the question *how environmental issues are framed within populist discourse in Swiss media over the past ten years*, focusing on the Swiss People's Party (SVP) and the Green Party. The project conducts a quantitative media analysis using a LLM to explore how the SVP and the Green Party engage with populist rhetoric when addressing environmental topics. The aim is to understand how both parties construct their narratives, position themselves in context of the people and elites, and use populist strategies to mobilize support or criticize opponents.

# Introduction

Over the past decade, environmental issues, especially those linked to climate change, have become central to political discourse around the world. In Switzerland, as in many other democracies, these topics are not only the subject of policy debates but are also increasingly shaped by populist rhetoric. Political parties across the ideological spectrum use media platforms to frame environmental concerns in ways that reflect their political agendas and mobilize their voter bases. This research project examines how the Swiss People’s Party (SVP), as a representative right-wing party, and the Green Party, as a representative left-wing party, engage in populist discourse on environmental issues in Swiss media.

This question is especially relevant in today’s polarized political climate, where environmental policies often become battlegrounds for broader ideological conflicts. Previous research (e.g. Kulin and Johansson 2024) has shown that right-wing populism tends to foster climate skepticism, whereas left-wing populism more often supports environmental action. These differences stem from how each variant of populism defines “the elite” and “the people.” Understanding how such dynamics play out in the media landscape can shed light on the role of political communication in shaping public attitudes toward climate policy.

Thus, this explorative research project investigates the following question: *How do the Swiss People's Party (SVP) and the Green Party present themselves in populist discourses on environmental issues, and how do their narratives differ?*

The entire project workflow was documented using version control via GitHub under the repository name *www.github.com/alessiarainone18/Populist-Narratives-on-Environmental-Issues,* which is publicly accessible. While the dataset itself is not published due to licensing restrictions, it can be made available upon request.

# Literature Review

-   What have others already done similar? \[all relevant sources should be available here\].
-   What am I doing differently from them?

# Theory

Theoretical argument and derive the hypotheses / models from it. If useful (e.g. because complex): Draw model.

![Theoretical model](modell.pdf){#fig-modell}

# Research Design

## Data Collection

The newspaper articles used in this study were collected via an API provided by *Swissdox*, a media archive platform hosted by the University of Zurich. Swissdox offers access to a comprehensive collection of Swiss print and online newspapers dating back over 50 years. The platform provides API documentation that enables users to programmatically access its database. As the API documentation was originally written in Python, it was necessary to translate the process into R. This step was supported by the language model ChatGPT-4.0, which assisted in adapting the example code provided in the documentation into functional R code.

Following a successful test run using the example API call, a custom API query was developed. This query included specific parameters, such as a keyword filter consisting of 35 German-language terms related to climate and environmental issues. The list of keywords was initially generated with the help of ChatGPT and subsequently reviewed for thematic relevance.

To narrow the scope to mainstream media coverage, the data collection was restricted to German-language articles from the following major Swiss news outlets: *Neue Zürcher Zeitung (NZZ)*, *20 Minuten*, *Blick*, *SRF*, and *Tages-Anzeiger*. While the initial time frame spanned 15 years (2009–2024), it was later restricted to the last 10 years (2014–2024), as it became apparent that some media sources only began contributing to the Swissdox archive several years after 2009.

In total, the initial API query returned over 87,000 articles. To refine the dataset and focus more specifically on the relevant unit of analysis, several filtering steps were applied. First, articles were manually filtered based on keywords referring to the Swiss People’s Party (SVP) and the Green Party, such as “SVP” and “Grüne.” In addition, only articles with a length between 300 and 2,000 words were retained to ensure a sufficient level of content for analysis while excluding overly short or excessively long texts.

Unnecessary metadata and variables delivered by the API were removed, and articles categorized under rubrics containing the term “international” were excluded, as the study focuses exclusively on environmental discourse within the Swiss national context. After applying these filters, the final dataset consisted of approximately 15,000 articles. From this corpus, a random sample of 2,500 articles was drawn. The analysis is conducted on this subset, which is considered representative of the overall sample and sufficient for drawing meaningful conclusions.

```{r ref.label=knitr::all_labels()}
#| echo: true 
#| eval: false


```

## Methods

### Quantitative Text Analysis via ChatGPT API

For the qualitative coding of populist framing and party positioning, the ChatGPT API (version 4.0) was used. Articles were evaluated based on a set of categories developed in collaboration with the model:

This framework allows for systematic comparison of populist discourses across parties and enables the identification of distinct rhetorical patterns in environmental narratives.

1.  <div>

    | **Category** | **Code** | **Description** |
    |------------------------|------------------------|------------------------|
    | **Relevance** | 1 | Relevant: Article discusses Swiss environmental politics |
    |  | 0 | Not relevant |
    | **Political Party Mentioned** | 1 | SVP (Swiss People's Party) |
    |  | 2 | JSVP (Young Swiss People's Party) |
    |  | 3 | GPS (Green Party of Switzerland) |
    |  | 4 | Junge Grüne (Young Green's) |
    |  | 99 | No or other party mentioned / not applicable |
    | **Support or Opposition** | 1 | Party expresses support for the environmental policy |
    |  | 2 | Party expresses opposition |
    |  | 99 | Unclear / not applicable |
    | **Framing Style** | 1 | Very pluralistic (diverse viewpoints, cooperative tone, evidence-based) |
    |  | 2 | Rather pluralistic |
    |  | 3 | Neutral |
    |  | 4 | Rather populistic (simplification, people vs. elite framing) |
    |  | 5 | Very populistic (strong anti-elite rhetoric, emotional tone, crisis framing) |
    |  | 99 | Not applicable |
    | **Definition of “Elite”** | 1 | Government / politicians |
    |  | 2 | Corporations / business elites |
    |  | 3 | Media / journalists |
    |  | 4 | Intellectuals / academics |
    |  | 5 | International organizations (e.g., EU, UN) |
    |  | 6 | Environmental activists / NGOs |
    |  | 99 | Other / not applicable |
    | **Definition of “The People”** | 1 | The Swiss population in general |
    |  | 2 | Workers / lower class |
    |  | 3 | Rural communities |
    |  | 4 | Traditional Swiss values group |
    |  | 5 | Small business owners / self-employed |
    |  | 6 | Farmers |
    |  | 99 | Other / not applicable |

    </div>

    ### 

    **Prompt Design**

    The first step in the process was the design of a prompt aimed at guiding OpenAI through the task of analyzing each article. The goal was to ensure that the model can systematically and clearly handle each article, following a step-by-step process. The prompt, which is available in the appendix, was written in simple language and divided into distinct tasks.

    The prompt consists of five main tasks from the category system as presented in the previous chapter.

    For each task and subtask, a corresponding code is provided. Additionally, a fallback code of 99 was introduced for instances where none of the categories apply, as the dataset includes a significant number of irrelevant articles. This prompt was initially tested within the ChatGPT 4.0 interface using a clearly populist article about the SVP. To ensure robustness, a set of randomly selected articles was also tested to identify any issues with the prompt's functionality. In cases where the prompt performed poorly, these examples were highlighted under each task to clarify for the AI how to proceed. Once the prompt was deemed sufficiently accurate, it was applied to the API for further testing.

    ### **Testing Phase**

    In the testing phase, five articles were randomly selected from the sample to be analyzed through the API. The API was configured to return the output in the form of a data table, with each variable as a column and the article number as a row. After conducting approximately five tests, it became apparent that many articles fell into the "not applicable" category, which led to the conclusion that adjustments to the prompt were necessary.

    Subsequent adjustments to the prompt were made to address this issue, refining the task definitions and ensuring more accurate categorization. The updated version of the prompt was then re-tested to confirm that it performed as expected.

# Results

Show results with plot, answer RQ

# Discussion

Discuss the results.

# Conclusion

What have we learned from this work (at best: and what not)? What would be next steps in this research?

# Bibliography {.unnumbered}

::: {#refs}
:::

# Appendix {.unnumbered}

```{r ref.label=knitr::all_labels()}
#| echo: true
#| eval: false

```
